Component response rate variation drives stability in large complex systems

### 2018-06-14 notebook/arxiv/ms.tex
Add acknowledgements
Thorough edits

\textbf{Figure 1: Example distribution of eigenvalues before (a) and
after (b) separating a randomly generated complex system into fast
(\(\boldsymbol{\gamma} = 1.95\)) and slow
(\(\boldsymbol{\gamma} = 0.05\)) component response rates.} Each panel
shows the same system where \(S = 200\), \(C = 0.05\), and
\(\sigma = 0.4\), and in each case \(E[\gamma] = 1\) (i.e., only the
distribution of \(\gamma\) differs between panels). \textbf{a.}
Eigenvalues plotted when all \(\gamma = 1\); distributions of points are
uniformly distributed within the grey circle with a radius of
\(\sigma\sqrt{SC} =\) 1.238 centred at -1 on the real axis. \textbf{b.}
Eigenvalues plotted when half \(\gamma = 1.95\) and half
\(\gamma = 0.05\); distributions of points can be partitioned into one
large circle of \(\sigma\sqrt{SC} =\) 1.718 centred at
\(\gamma = -1.95\) and one small circle of \(\sigma\sqrt{SC} =\) 0.044
centred at \(\gamma = -0.05\). In a, the maximum real eigenvalue
\(\max\left(\Re(\lambda)\right) =\) 0.2344871, while in b
\(\max\left(\Re(\lambda)\right) =\) -0.0002273135, meaning that the
complex system in b but not a is stable because in b
\(\max\left(\Re(\lambda)\right) < 0\). In 1 million randomly generated
complex systems under the same parameter values, 1 was stable when
\(\gamma = 1\) while 32 were stable when \(\gamma = \{1.95, 0.05\}\).
Overall, complex systems that are separated into fast versus slow
components tend to be more stable than otherwise identical systems with
identical component response rates.

@@

Rows in \(M\) define how a given component \(i\) is affected by other
components of the system, meaning that the rate of component response
time can be modelled by multiplying all row elements by a real scalar
value
\(\gamma_{i}\)\textsuperscript{\protect\hyperlink{ref-Patel2018}{14}}.
The distribution of \(\gamma\) over \(S\) components thereby models the
distribution of component response rates. An instructive example
compares one \(M\) where \(\gamma_{i} = 1\) for all \(i\) in \(S\) to
the same \(M\) when half of \(\gamma_{i} = 1.95\) and half of
\(\gamma_{i} = 0.05\). This models one system in which \(\gamma\) is
invariant and one in which \(\gamma\) varies, but systems are otherwise
identical (note \(E[\gamma_{i}] = 1\) in both cases). I assume
\(S = 200\), \(C = 0.05\), and \(\sigma = 0.4\); diagonal elements are
set to \(-1\) and non-zero off-diagonal elements are drawn randomly from
\(\mathcal{N}(0, \sigma^{2})\). Rows are then multiplied by
\(\gamma_{i}\) to generate \(M\). When \(\gamma_{i} = 1\), eigenvalues
of \(M\) are distributed uniformly within a circle centred at
(\(-1, 0\)) with a radius of 1.265 (Fig. 1a). Hence, the real components
of eigenvalues are highly unlikely to all be negative when all
\(\gamma_{i} = 1\). But when \(\gamma_{i}\) values are separated into
two groups, eigenvalues are no longer uniformly distributed (Fig. 1b).
Instead, two distinct clusters of eigenvalues appear (grey circles in
Fig. 1b), one centred at (\(-1.95, 0\)) and the other centred at
(\(-0.05, 0\)). The former has a large radius, but the real components
have shifted to the left (in comparison to when \(\gamma = 1\)) and all
\(\Re({\lambda}) < 0\). The latter cluster has real components that have
shifted to the right, but has a smaller radius. Overall, for 1 million
randomly assembled \(M\), this division between slow and fast component
response rates results in more stable systems: 1 stable given
\(\gamma = 1\) versus 32 stable given \(\gamma = \{1.95, 0.5\}\).

@@

\textbf{Figure 2: Distributions of eigenvalues before (a) and after (b)
introducing variation in component response rate
(\(\boldsymbol{\gamma}\)) in complex systems.} Each panel show the same
system where \(S = 1000\), \(C = 1\), and \(\sigma = 0.4\). \textbf{a.}
Eigenvalues plotted in the absence of \(Var(\gamma)\) where
\(E[\gamma] = 1\), versus \textbf{b.} eigenvalues plotted given
\(\gamma \sim \mathcal{U}(0, 2)\), which increases the variance of
interaction strengths (\(\sigma^{2}\)) but clusters eigenvalues toward
the distribution's centre (-1, 0). Black and red elipses in both panels
show the circle centred on the distribution in panels a and b,
respectively, which have a radius of \(\sigma \sqrt{SC}\). Proportions
of \(\Re(\lambda) < 0\) are 0.548 and 0.552 for a and b, respectively.

@@

\textbf{Figure 3: Stability of large complex systems with and without
variation in component response rate(\(\boldsymbol{\gamma}\)).} The
\(\ln\) number of systems that are stable across different system sizes
(\(S\)) given \(C = 1\), and the proportion of systems in which
variation in \(\gamma\) is critical for system stability. For each
\(S\), 1 million complex systems are randomly generated. Stability of
each complex system is tested given variation in \(\gamma\) by randomly
sampling \(\gamma \sim \mathcal{U}(0, 2)\). Stability given
\(Var(\gamma)\) is then compared to stability in an otherwise identical
system in which \(\gamma = E[\mathcal{U}(0, 2)]\) for all components.
Light and dark grey bars show the number of stable systems in the
absence and presence of \(Var(\gamma)\), respectively. The black line
shows the proportion of systems that are stable when
\(Var(\gamma) > 0\), but would be unstable if \(Var(\gamma) = 0\).

@@

To further investigate the potential of \(Var(\gamma)\) to be stabilising,
I used a genetic algorithm (the space of possible \(\gamma\)
values was too large to search
exhaustively\textsuperscript{\protect\hyperlink{ref-Hamblin2013}{18}};
see \hyperlink{SIstart}{Supplementary Information}). For each of 10000 
random \(M\), the
genetic algorithm initialised 1000 different sets of
\(\gamma \sim \mathcal{U}(0, 2)\) values of size \(S\). Eigenanalysis was
performed on \(M\) using 
each set of \(\gamma\) values, and the 20 sets with the
lowest \(\max\left(\Re(\lambda)\right)\) each produced 50 clonal offspring with
subsequent mutation and crossover between the resulting new population
of 1000 \(\gamma\) sets. The genetic algorithm terminated if a stable
\(M\) was found, 20 generations occurred, or a convergence criteria of
minimum fitness increase between generations was satisfied. Across
\(S = \{2, 3, ..., 39, 40\}\), sets of \(\gamma\) values were found that
resulted in stable systems with probabilities that were orders of
magnitude higher than when \(\gamma = 1\) (see \hyperlink{SIstart}{Supplementary
Information}), meaning that stability could often be achieved by 
manipulating \(S\) \(\gamma\) values rather than \(S \times S\) \(M\) elements.
Hence, managing the response rates of system components in a targetted
way can potentially facilitate the stabilisation of complex systems 
through a reduction in dimensionality.

I have focused broadly on random complex systems, but it is also
worthwhile to consider more restricted interactions such as those of
specific ecological
networks\textsuperscript{\protect\hyperlink{ref-Allesina2012}{2}}. These
include systems in which all interactions are negative (competitive networks), positive (mutualist networks), or \(i\) and
\(j\) pairs have opposing signs (predator-prey networks). In
general, competitive and mutualist networks tend to be destabilising,
and predator-prey network tend to be
stabilising\textsuperscript{\protect\hyperlink{ref-Allesina2011}{19}}.
When \(Var(\gamma)\) is applied to each, the proportion of stable
competitive and predator-prey networks increases, but the proportion of
stable mutualist networks does not (see 
\hyperlink{SIstart}{Supplementary Information}).
Additionally, when each component of \(M\) is interpreted as a unique
species and given a random intrinsic growth
rate\textsuperscript{\protect\hyperlink{ref-Dougoud2018}{20}},
feasibility is not increased by \(Var(\gamma)\), suggesting that
variation in species generation time might be unlikely to drive
stability in purely multi-species networks (see \hyperlink{SIstart}{Supplementary
Information}).

@@

I am supported by a Leverhulme Trust Early Career Fellowship (ECF-2016-376).
Conversations with L. Bussi\`ere and N. Bunnefeld improved the quality of
this work.

@@

\begin{longtable}[]{@{}llllll@{}}
\toprule
N & A0\_unstable & A0\_stable & A1\_unstable & A1\_stable &
A1\_stabilised\tabularnewline
\midrule
\endhead
2 & 48 & 99952 & 48 & 99952 & 0\tabularnewline
3 & 229 & 99771 & 231 & 99769 & 0\tabularnewline
4 & 701 & 99299 & 704 & 99296 & 0\tabularnewline
5 & 1579 & 98421 & 1587 & 98413 & 0\tabularnewline
6 & 3218 & 96782 & 3253 & 96747 & 6\tabularnewline
7 & 5519 & 94481 & 5619 & 94381 & 23\tabularnewline
8 & 9062 & 90938 & 9237 & 90763 & 77\tabularnewline
9 & 13436 & 86564 & 13729 & 86271 & 230\tabularnewline
10 & 18911 & 81089 & 19303 & 80697 & 505\tabularnewline
11 & 25594 & 74406 & 25961 & 74039 & 1011\tabularnewline
12 & 33207 & 66793 & 33382 & 66618 & 1724\tabularnewline
13 & 41160 & 58840 & 41089 & 58911 & 2655\tabularnewline
14 & 50575 & 49425 & 49894 & 50106 & 3777\tabularnewline
15 & 59250 & 40750 & 57892 & 42108 & 4824\tabularnewline
16 & 67811 & 32189 & 65740 & 34260 & 5634\tabularnewline
17 & 75483 & 24517 & 73056 & 26944 & 5943\tabularnewline
18 & 82551 & 17449 & 79878 & 20122 & 5780\tabularnewline
19 & 88030 & 11970 & 85204 & 14796 & 5417\tabularnewline
20 & 92254 & 7746 & 89766 & 10234 & 4544\tabularnewline
21 & 95233 & 4767 & 93002 & 6998 & 3695\tabularnewline
22 & 97317 & 2683 & 95451 & 4549 & 2803\tabularnewline
23 & 98508 & 1492 & 97122 & 2878 & 1991\tabularnewline
24 & 99240 & 760 & 98407 & 1593 & 1216\tabularnewline
25 & 99669 & 331 & 99082 & 918 & 739\tabularnewline
26 & 99871 & 129 & 99490 & 510 & 452\tabularnewline
27 & 99938 & 62 & 99732 & 268 & 240\tabularnewline
28 & 99985 & 15 & 99888 & 112 & 108\tabularnewline
29 & 99990 & 10 & 99951 & 49 & 46\tabularnewline
30 & 100000 & 0 & 99981 & 19 & 19\tabularnewline
31 & 100000 & 0 & 99993 & 7 & 7\tabularnewline
32 & 100000 & 0 & 99996 & 4 & 4\tabularnewline
33 & 100000 & 0 & 99998 & 2 & 2\tabularnewline
34 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} &
\ldots{}\tabularnewline
50 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llllll@{}}
\toprule
N & A0\_unstable & A0\_stable & A1\_unstable & A1\_stable &
A1\_stabilised\tabularnewline
\midrule
\endhead
2 & 56 & 99944 & 56 & 99944 & 0\tabularnewline
3 & 3301 & 96699 & 3301 & 96699 & 0\tabularnewline
4 & 34446 & 65554 & 34446 & 65554 & 0\tabularnewline
5 & 86520 & 13480 & 86520 & 13480 & 0\tabularnewline
6 & 99683 & 317 & 99683 & 317 & 0\tabularnewline
7 & 99998 & 2 & 99998 & 2 & 0\tabularnewline
8 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
9 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
10 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
11 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
12 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} &
\ldots{}\tabularnewline
50 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\bottomrule
\end{longtable}

>>>>

\textbf{Figure 1: Example distribution of eigenvalues before (a) and
after (b) separating a randomly generated complex system into fast
(\(\boldsymbol{\gamma} = 1.95\)) and slow
(\(\boldsymbol{\gamma} = 0.05\)) component response rates.} Each panel
shows the same system where \(S = 200\), \(C = 0.05\), and
\(\sigma = 0.4\), and in each case \(E[\gamma] = 1\) (i.e., only 
\(Var(\gamma)\) differs between panels). \textbf{a.}
Eigenvalues plotted when all \(\gamma = 1\); points are
uniformly distributed within the grey circle with a radius of
\(\sigma\sqrt{SC} =\) 1.238 centred at -1 on the real axis. \textbf{b.}
Eigenvalues plotted when half \(\gamma = 1.95\) and half
\(\gamma = 0.05\); distributions of points can be partitioned into one
large circle with a radius of \(\sigma\sqrt{SC} =\) 1.718 centred at
\(\gamma = -1.95\) and one small circle with a radius of
\(\sigma\sqrt{SC} =\) 0.044
centred at \(\gamma = -0.05\). In a, the maximum real eigenvalue
\(\max\left(\Re(\lambda)\right) =\) 0.2344871, while in b
\(\max\left(\Re(\lambda)\right) =\) -0.0002273135, meaning that the
complex system in b but not a is stable because in b
\(\max\left(\Re(\lambda)\right) < 0\). In 1 million randomly generated
complex systems under the same parameter values, 1 was stable when
\(\gamma = 1\) while 32 were stable when \(\gamma = \{1.95, 0.05\}\).
Overall, complex systems that are separated into fast versus slow
components tend to be more stable than otherwise identical systems with
identical component response rates.

@@

Rows in \(M\) define how a given component \(i\) is affected by other
components of the system, meaning that the rate of component response
time can be modelled by multiplying all row elements by a real scalar
value
\(\gamma_{i}\)\textsuperscript{\protect\hyperlink{ref-Patel2018}{14}} (see 
\hyperlink{SIstart}{Supplementary Information} for details).
The distribution of \(\gamma\) over \(S\) components thereby models the
distribution of component response rates. An instructive example
compares one \(M\) when \(\gamma_{i} = 1\) for all \(i\) in \(S\) to
the same \(M\) when half of \(\gamma_{i} = 1.95\) and half of
\(\gamma_{i} = 0.05\). This models one system in which \(\gamma\) is
invariant and one in which \(\gamma\) varies, but systems are otherwise
identical (note \(E[\gamma_{i}] = 1\) in both cases). I assume
\(S = 200\), \(C = 0.05\), and \(\sigma = 0.4\); diagonal elements are
set to \(-1\) and non-zero off-diagonal elements are drawn randomly from
\(\mathcal{N}(0, \sigma^{2})\). Rows are then multiplied by
\(\gamma_{i}\) to generate \(M\). When \(\gamma_{i} = 1\), eigenvalues
of \(M\) are distributed uniformly within a circle centred at
(\(-1, 0\)) with a radius of 1.265 (Fig. 1a). Hence, the real components
of eigenvalues are highly unlikely to all be negative when all
\(\gamma_{i} = 1\). But when \(\gamma_{i}\) values are separated into
two groups, eigenvalues are no longer uniformly distributed (Fig. 1b).
Instead, two distinct clusters of eigenvalues appear (grey circles in
Fig. 1b), one centred at (\(-1.95, 0\)) and the other centred at
(\(-0.05, 0\)). The former has a large radius, but the real components
have shifted to the left (in comparison to when \(\gamma = 1\)) and all
\(\Re({\lambda}) < 0\). The latter cluster has real components that have
shifted to the right, but has a smaller radius. Overall, for 1 million
randomly assembled \(M\), this division between slow and fast component
response rates results in more stable systems: 1 stable given
\(\gamma = 1\) versus 32 stable given \(\gamma = \{1.95, 0.5\}\).

@@

\textbf{Figure 2: Distributions of eigenvalues before (a) and after (b)
introducing variation in component response rate
(\(\boldsymbol{\gamma}\)) in complex systems.} Each panel shows the same
system where \(S = 1000\), \(C = 1\), and \(\sigma = 0.4\). \textbf{a.}
Eigenvalues plotted in the absence of \(Var(\gamma)\) where
\(E[\gamma] = 1\), versus \textbf{b.} eigenvalues plotted given
\(\gamma \sim \mathcal{U}(0, 2)\), which increases the variance of
interaction strengths (\(\sigma^{2}\)) but clusters eigenvalues toward
the distribution's centre (-1, 0). Black and red elipses in both panels
show the circle centred on the distribution in panels a and b,
respectively, which have a radius of \(\sigma \sqrt{SC}\). Proportions
of \(\Re(\lambda) < 0\) are 0.548 and 0.552 for a and b, respectively.

@@

\textbf{Figure 3: Stability of large complex systems with and without
variation in component response rate(\(\boldsymbol{\gamma}\)).} Y-axes show
the \(\ln\) number of systems that are stable across different system sizes
(\(S\)) given \(C = 1\) (left axis), and the proportion of systems in which
variation in \(\gamma\) is critical for system stability (right axis). For each
\(S\), 1 million complex systems are randomly generated. Stability of
each complex system is tested given variation in \(\gamma\) by randomly
sampling \(\gamma \sim \mathcal{U}(0, 2)\). Stability given
\(Var(\gamma)\) is then compared to stability in an otherwise identical
system in which \(\gamma = E[\mathcal{U}(0, 2)]\) for all components.
Light and dark grey bars show the number of stable systems in the
absence versus presence of \(Var(\gamma)\), respectively. The black line
shows the proportion of systems that are stable when
\(Var(\gamma) > 0\), but would be unstable if \(Var(\gamma) = 0\).

@@

To further investigate the potential of \(Var(\gamma)\) to be stabilising,
I used a genetic algorithm (the space of possible \(\gamma\)
values was too large to search
exhaustively\textsuperscript{\protect\hyperlink{ref-Hamblin2013}{18}};
see \hyperlink{SIstart}{Supplementary Information}). For each of 10000 
random \(M\), the
genetic algorithm initialised 1000 different sets of
\(\gamma \sim \mathcal{U}(0, 2)\) values of size \(S\). Eigenanalysis was
performed on \(M\) using 
each set of \(\gamma\) values, and the 20 sets with the
lowest \(\max\left(\Re(\lambda)\right)\) each produced 50 clonal offspring with
subsequent mutation and crossover between the resulting new population
of 1000 \(\gamma\) sets. The genetic algorithm terminated if a stable
\(M\) was found, 20 generations occurred, or a convergence criteria of
minimum fitness increase between generations was satisfied. Across
\(S = \{2, 3, ..., 39, 40\}\), sets of \(\gamma\) values were found that
resulted in stable systems with probabilities that were up to four orders of
magnitude higher than when \(\gamma = 1\) (see \hyperlink{SIstart}{Supplementary
Information}), meaning that stability could often be achieved by 
manipulating \(S\) \(\gamma\) values rather than \(S \times S\) \(M\) elements.
Hence, managing the response rates of system components in a targetted
way can potentially facilitate the stabilisation of complex systems 
through a reduction in dimensionality.

I have focused broadly on random complex systems, but it is also
worthwhile to consider more restricted interactions such as those of
specific ecological
networks\textsuperscript{\protect\hyperlink{ref-Allesina2012}{2}}. These
include systems in which all interactions are negative (competitive networks), positive (mutualist networks), or \(i\) and
\(j\) pairs have opposing signs (predator-prey networks). In
general, competitive and mutualist networks tend to be destabilising,
and predator-prey networks tend to be
stabilising\textsuperscript{\protect\hyperlink{ref-Allesina2011}{19}}.
When \(Var(\gamma)\) is applied to each, the proportion of stable
competitive and predator-prey networks increases, but the proportion of
stable mutualist networks does not (see 
\hyperlink{SIstart}{Supplementary Information}).
Additionally, when each component of \(M\) is interpreted as a unique
species and given a random intrinsic growth
rate\textsuperscript{\protect\hyperlink{ref-Dougoud2018}{20}},
feasibility is not increased by \(Var(\gamma)\), suggesting that
variation in species generation time might be unlikely to drive
stability in purely multi-species networks (see \hyperlink{SIstart}{Supplementary
Information}).

@@

I am supported by a Leverhulme Trust Early Career Fellowship (ECF-2016-376).
Conversations with L. Bussi\`ere and N. Bunnefeld, and helpful comments from
J. J. Cusack and I. L. Jones, improved the quality of this work.

@@

\begin{longtable}[]{@{}llllll@{}}
\toprule
N & A0\_unstable & A0\_stable & A1\_unstable & A1\_stable &
A1\_stabilised\tabularnewline
\midrule
\endhead
2 & 48 & 99952 & 48 & 99952 & 0\tabularnewline
3 & 229 & 99771 & 231 & 99769 & 0\tabularnewline
4 & 701 & 99299 & 704 & 99296 & 0\tabularnewline
5 & 1579 & 98421 & 1587 & 98413 & 0\tabularnewline
6 & 3218 & 96782 & 3253 & 96747 & 6\tabularnewline
7 & 5519 & 94481 & 5619 & 94381 & 23\tabularnewline
8 & 9062 & 90938 & 9237 & 90763 & 77\tabularnewline
9 & 13436 & 86564 & 13729 & 86271 & 230\tabularnewline
10 & 18911 & 81089 & 19303 & 80697 & 505\tabularnewline
11 & 25594 & 74406 & 25961 & 74039 & 1011\tabularnewline
12 & 33207 & 66793 & 33382 & 66618 & 1724\tabularnewline
13 & 41160 & 58840 & 41089 & 58911 & 2655\tabularnewline
14 & 50575 & 49425 & 49894 & 50106 & 3777\tabularnewline
15 & 59250 & 40750 & 57892 & 42108 & 4824\tabularnewline
16 & 67811 & 32189 & 65740 & 34260 & 5634\tabularnewline
17 & 75483 & 24517 & 73056 & 26944 & 5943\tabularnewline
18 & 82551 & 17449 & 79878 & 20122 & 5780\tabularnewline
19 & 88030 & 11970 & 85204 & 14796 & 5417\tabularnewline
20 & 92254 & 7746 & 89766 & 10234 & 4544\tabularnewline
21 & 95233 & 4767 & 93002 & 6998 & 3695\tabularnewline
22 & 97317 & 2683 & 95451 & 4549 & 2803\tabularnewline
23 & 98508 & 1492 & 97122 & 2878 & 1991\tabularnewline
24 & 99240 & 760 & 98407 & 1593 & 1216\tabularnewline
25 & 99669 & 331 & 99082 & 918 & 739\tabularnewline
26 & 99871 & 129 & 99490 & 510 & 452\tabularnewline
27 & 99938 & 62 & 99732 & 268 & 240\tabularnewline
28 & 99985 & 15 & 99888 & 112 & 108\tabularnewline
29 & 99990 & 10 & 99951 & 49 & 46\tabularnewline
30 & 100000 & 0 & 99981 & 19 & 19\tabularnewline
31 & 100000 & 0 & 99993 & 7 & 7\tabularnewline
32 & 100000 & 0 & 99996 & 4 & 4\tabularnewline
33 & 100000 & 0 & 99998 & 2 & 2\tabularnewline
34 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} \tabularnewline
50 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llllll@{}}
\toprule
N & A0\_unstable & A0\_stable & A1\_unstable & A1\_stable &
A1\_stabilised\tabularnewline
\midrule
\endhead
2 & 56 & 99944 & 56 & 99944 & 0\tabularnewline
3 & 3301 & 96699 & 3301 & 96699 & 0\tabularnewline
4 & 34446 & 65554 & 34446 & 65554 & 0\tabularnewline
5 & 86520 & 13480 & 86520 & 13480 & 0\tabularnewline
6 & 99683 & 317 & 99683 & 317 & 0\tabularnewline
7 & 99998 & 2 & 99998 & 2 & 0\tabularnewline
8 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
9 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
10 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
11 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
12 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} \tabularnewline
50 & 100000 & 0 & 100000 & 0 & 0\tabularnewline
\bottomrule
\end{longtable}
